---
title: "Prueba"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message = FALSE,warning = FALSE)
```

```{r,echo = FALSE, cache = FALSE, message = FALSE,warning = FALSE}
library(tidyverse)
library(tidymodels)
library(tidytext)
library(skimr)
library(scales)
library(ggrepel)
library(skimr)
library(vip)
theme_set(theme_classic())
```



## Import Data Set


```{r}
data<-read.csv('../input/dataset_diabetes/diabetic_data.csv')
```

Some features and Databases Design


```{r}
data<-data%>%
  mutate_if(is.character,as.factor)
```

## EDA

```{r}
data%>%
  group_by(race)%>%
  count(sort = TRUE)%>%
  filter(race!='?')%>%
  ungroup()%>%
  mutate(perc=n/sum(n))%>%
  mutate(race=fct_reorder(race,n))%>%
  ggplot(aes(reorder(race,perc),perc, fill=race))+
  geom_col(show.legend = FALSE)+
  scale_y_continuous(labels = percent)+
  coord_flip()+
  labs(title = 'Percent Distribution per Race',
       x='',
       y='Total')
```


```{r}
data%>%
  group_by(race,gender,medical_specialty)%>%
  count(sort = TRUE)%>%
  filter(race!='?',
         medical_specialty!='?',
         gender!='Unknown/Invalid')%>%
  ungroup()%>%
  ggplot(aes(race,n,fill=medical_specialty))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~gender)
```



```{r}
top_medial_specialty<-data%>%
  filter(medical_specialty!='?')%>%
  count(medical_specialty,sort = TRUE)%>%
  top_n(10)
```


```{r}
data%>%
  group_by(race,gender,medical_specialty)%>%
  count(sort = TRUE)%>%
  filter(race!='?',
         medical_specialty!='?',
         gender!='Unknown/Invalid',
         medical_specialty %in% top_medial_specialty$medical_specialty)%>%
  ungroup()%>%
  mutate(race=reorder_within(race,n,medical_specialty))%>%
  ggplot(aes(race,n,fill=gender))+
  geom_bar(stat = 'identity')+
  scale_x_reordered()+
  coord_flip()+
  facet_wrap(~medical_specialty,scales = 'free_y')+
  theme(strip.text = element_text(size=4))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title = 'Relation Between Medical Specialty per Gender - Race',
       subtitle = 'Top 10 in Medical Specialty',
       x='',
       y='Total',
       fill='Gender')
```


```{r}
data%>%
  count(readmitted,sort = TRUE)%>%
  mutate(perc=round(n/sum(n),2))%>%
  ggplot(aes(readmitted,perc))+
  geom_col()+
  scale_y_continuous(labels = percent)+
  coord_flip()+
  labs(title = 'Readmitted Frecuency')
```
This is the First Feature
```{r}
data<-data%>%
  mutate(diag_1=str_replace_all(diag_1,"[?]",'0'),
    diag_2=str_replace_all(diag_2,"[?]",'0'),
    diag_3=str_replace_all(diag_3,"[?]",'0'),
    weight=str_replace_all(weight,'[?]','0'))%>%
  filter(medical_specialty!='?',
         race!='?')%>%
  mutate(readmitted=if_else(readmitted=='NO','NO','YES'))
```



```{r}
data%>%
  count(race)
```


```{r}
# data%>%
#   mutate(diag_1=as.numeric(diag_1),
#          diag_2=as.numeric(diag_2),
#          diag_3=as.numeric(diag_3))%>%
#   mutate(readmitted=if_else(readmitted=='NO','NO','YES'))%>%
#   select(race,medical_specialty,diag_1:diag_3,change:readmitted)%>%
#   janitor::clean_names()%>%
#   filter(medical_specialty!='?',
#          race!='?',
#          medical_specialty %in% top_medial_specialty$medical_specialty)%>%
#   pivot_longer(diag_1:diag_3,names_to='Diagnosis',values_to='Measure')%>%
#   group_by(race,medical_specialty,readmitted)%>%
#   summarize(avg_measure=mean(Measure))%>%
#   ungroup()
```


```{r}
data%>%
  mutate(diag_1=as.numeric(diag_1),
         diag_2=as.numeric(diag_2),
         diag_3=as.numeric(diag_3))%>%
  na.omit()%>%
  mutate(readmitted=if_else(readmitted=='NO','NO','YES'))%>%
  select(medical_specialty,diag_1:diag_3,change:readmitted)%>%
  janitor::clean_names()%>%
  filter(medical_specialty!='?',
         medical_specialty %in% top_medial_specialty$medical_specialty)%>%
  pivot_longer(diag_1:diag_3,names_to='Diagnosis',values_to='Measure')%>%
  group_by(medical_specialty,readmitted)%>%
  summarize(avg_measure=mean(Measure))%>%
  ungroup()%>%
  mutate(medical_specialty=reorder_within(medical_specialty,avg_measure,readmitted))%>%
  ggplot(aes(avg_measure,medical_specialty,color=readmitted))+
  geom_errorbar(aes(xmin=0,xmax=avg_measure),width= 0,linetype='dashed')+
  geom_point(aes(size=avg_measure),show.legend = FALSE)+
  scale_y_reordered()+
  guides(color=FALSE)+
  facet_wrap(~readmitted,scales = 'free')+
  labs(title = 'Relation Between Type of medical care and Readmitted Status',
       x='Diagnostincs Measure',
       y='')
```

Admission sickness relationships do not represent the pattern on readmission.





```{r}
data_select<-data%>%
 filter(weight!='0')%>%
  select(race:weight,medical_specialty,num_lab_procedures:number_inpatient,number_diagnoses,metformin:readmitted)
  
```


```{r}
data_select%>%
  filter(race=='Caucasian')%>%
  ggplot(aes(age,weight,color=readmitted))+
  geom_point()+
  facet_wrap(~readmitted)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```


* Weight-age relationship at readmission positive;



```{r}
data_select%>%
  group_by(race,gender,age,weight,medical_specialty,readmitted)%>%
  count(sort=TRUE)
```



```{r}
data_select%>%
  group_by(race,gender,age,weight,medical_specialty,readmitted)%>%
  count(sort=TRUE)%>%
  filter(race=='Caucasian')%>%
  group_by(medical_specialty)%>%
  top_n(5,n)%>%
  ggplot(aes(age,
             n,
             size=weight,
             color=factor(gender)))+
  geom_point()+
  geom_text_repel(aes(label=medical_specialty))+
  facet_wrap(~readmitted, scales = 'free')+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

By Gender
```{r}
data_select%>%
  group_by(race,gender,age,weight,medical_specialty,readmitted)%>%
  count(sort=TRUE)%>%
  filter(race=='Caucasian',
         gender=='Female',
         medical_specialty %in% top_medial_specialty$medical_specialty)%>%
  group_by(medical_specialty)%>%
  #top_n(20,n)%>%
  distinct(medical_specialty,age,.keep_all = TRUE)%>%
  ggplot(aes(n,
             age,
             size=weight,
             color=factor(medical_specialty)))+
  geom_point()+
  geom_text_repel(aes(label=medical_specialty),force = TRUE)+
  guides(color=FALSE)+
  facet_wrap(~readmitted, scales = 'free_x')+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title = 'Relation Medical Traitment - Readmition',
       subtitle = 'Female Case',
       y='',
       x='Total')
```


```{r}
data_select%>%
  group_by(race,gender,age,weight,medical_specialty,readmitted)%>%
  count(sort=TRUE)%>%
  filter(race=='Caucasian',
         gender!='Female',
         medical_specialty %in% top_medial_specialty$medical_specialty)%>%
  group_by(medical_specialty)%>%
  #top_n(20,n)%>%
  distinct(medical_specialty,age,.keep_all = TRUE)%>%
  ggplot(aes(n,
             age,
             size=weight,
             color=medical_specialty))+
  geom_point()+
  geom_text_repel(aes(label=medical_specialty),force = TRUE)+
  facet_wrap(~readmitted, scales = 'free_x')+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title = 'Relation Medical Traitment - Readmition',
       subtitle = 'Male Case',
       y='',
       x='Total')
```



```{r}
casuas<-data_select%>%
  #filter(medical_specialty %in% top_medial_specialty$medical_specialty)%>%
  group_by(race,age,weight,medical_specialty,readmitted)%>%
  count(sort=TRUE)%>%
  filter(n>4,
         race=='Caucasian',
         readmitted=='YES')%>%
  distinct(medical_specialty,age,.keep_all = TRUE)%>%
  group_by(medical_specialty,age)%>%
  summarize(avg_readmition = mean(n))%>%
  mutate(age=reorder_within(age,avg_readmition,medical_specialty))%>%
  mutate(mean_medial=mean(avg_readmition))%>%
  ungroup()
casuas%>%
  ggplot(aes(avg_readmition,age,color=medical_specialty))+
  geom_vline(data = casuas,mapping = aes(xintercept=mean_medial))+
  geom_errorbar(aes(xmin=mean_medial,xmax=avg_readmition),width= 0,linetype='dashed')+
  geom_point(aes(size=avg_readmition),show.legend = FALSE)+
  scale_y_reordered()+
  facet_wrap(~medical_specialty,scales = 'free')
  
```



```{r}
casuas<-data_select%>%
  #filter(medical_specialty %in% top_medial_specialty$medical_specialty)%>%
  group_by(race,age,weight,medical_specialty,readmitted)%>%
  count(sort=TRUE)%>%
  filter(n>4,
         race=='Caucasian',
         readmitted!='YES')%>%
  distinct(medical_specialty,age,.keep_all = TRUE)%>%
  group_by(medical_specialty,age)%>%
  summarize(avg_readmition = mean(n))%>%
  mutate(age=reorder_within(age,avg_readmition,medical_specialty))%>%
  mutate(mean_medial=mean(avg_readmition))%>%
  ungroup()
casuas%>%
  ggplot(aes(avg_readmition,age,color=medical_specialty))+
  geom_vline(data = casuas,mapping = aes(xintercept=mean_medial))+
  geom_errorbar(aes(xmin=mean_medial,xmax=avg_readmition),width= 0,linetype='dashed')+
  geom_point(aes(size=avg_readmition),show.legend = FALSE)+
  scale_y_reordered()+
  facet_wrap(~medical_specialty,scales = 'free')
  
```

```{r}
data_select%>%
  count(race)
```



```{r}
data_select%>%
  filter(readmitted=='YES')%>%
  group_by(medical_specialty,race,age)%>%
  count(sort=TRUE)%>%
  summarize(avg_readmitted=mean(n))%>%
  arrange(desc(avg_readmitted))%>%
  ungroup()%>%
  mutate(medical_specialty=reorder_within(medical_specialty,avg_readmitted,race))%>%
  ggplot(aes(avg_readmitted,medical_specialty,color=age))+
  geom_point(aes(size=avg_readmitted))+
  scale_y_reordered()+
  facet_wrap(~race, scales = 'free',nrow = 3)

```
```{r}
data_select%>%
  filter(readmitted!='YES')%>%
  group_by(medical_specialty,race,age)%>%
  count(sort=TRUE)%>%
  filter(n>2,
         age!='[20-30)')%>%
  summarize(avg_readmitted=mean(n))%>%
  arrange(desc(avg_readmitted))%>%
  ungroup()%>%
  mutate(medical_specialty=reorder_within(medical_specialty,avg_readmitted,age))%>%
  ggplot(aes(avg_readmitted,medical_specialty,color=medical_specialty))+
  geom_point(aes(size=avg_readmitted))+
  scale_y_reordered()+
  guides(color=FALSE,
         size=FALSE)+
  facet_wrap(~age, scales = 'free',nrow = 3)
```

```{r}
data_select%>%
  filter(readmitted=='YES')%>%
  group_by(medical_specialty,race,age)%>%
  count(sort=TRUE)%>%
  filter(n>2,
         age!='[20-30)',
         race=='Caucasian')%>%
  summarize(avg_readmitted=mean(n))%>%
  arrange(desc(avg_readmitted))%>%
  ungroup()%>%
  mutate(medical_specialty=reorder_within(medical_specialty,avg_readmitted,age))%>%
  ggplot(aes(avg_readmitted,medical_specialty,color=medical_specialty))+
  geom_point(aes(size=avg_readmitted))+
  scale_y_reordered()+
  guides(color=FALSE,
         size=FALSE)+
  facet_wrap(~age, scales = 'free',nrow = 3)
```

```{r}
data_select%>%
  filter(readmitted=='YES')%>%
  group_by(medical_specialty,race,weight)%>%
  count(sort=TRUE)%>%
  filter(n>2)%>%
  summarize(avg_readmitted=mean(n))%>%
  arrange(desc(avg_readmitted))%>%
  ungroup()%>%
  mutate(medical_specialty=reorder_within(medical_specialty,avg_readmitted,weight))%>%
  ggplot(aes(avg_readmitted,medical_specialty,color=race))+
  geom_point(aes(size=avg_readmitted))+
  scale_y_reordered()+
  guides(size=FALSE)+
  facet_wrap(~weight, scales = 'free',nrow = 3)
```



```{r}
data_select%>%
  filter(readmitted!='YES')%>%
  group_by(medical_specialty,race,weight)%>%
  count(sort=TRUE)%>%
  filter(n>2)%>%
  summarize(avg_readmitted=mean(n))%>%
  arrange(desc(avg_readmitted))%>%
  ungroup()%>%
  mutate(medical_specialty=reorder_within(medical_specialty,avg_readmitted,weight))%>%
  ggplot(aes(avg_readmitted,medical_specialty,color=race))+
  geom_point(aes(size=avg_readmitted))+
  scale_y_reordered()+
  guides(size=FALSE)+
  facet_wrap(~weight, scales = 'free',nrow = 3)
```

## Build Model and Machine Learning Interpretability

```{r}
data_select$readmitted<-as.factor(data_select$readmitted)
set.seed(1234)
readmitted_split <- initial_split(data_select, strata = readmitted)
readmitted_train <- training(readmitted_split)
readmitted_test <- testing(readmitted_split)
```

```{r}
readmitted_rec <- recipe(readmitted ~ ., data = readmitted_train) %>%
    step_normalize(all_numeric())%>%
    step_other(num_lab_procedures, num_procedures,threshold = 0.005)%>%
    step_downsample(readmitted)

tree_prep <- prep(readmitted_rec)
juiced <- juice(tree_prep)
```


```{r}
tune_spec <- rand_forest(
  mtry = tune(),
  trees = 1000,
  min_n = tune()
) %>%
  set_mode("classification") %>%
  set_engine("ranger")

tune_wf <- workflow() %>%
  add_recipe(readmitted_rec) %>%
  add_model(tune_spec)
```



```{r}
set.seed(234)
readmitted_folds <- vfold_cv(readmitted_train)
doParallel::registerDoParallel()

set.seed(345)
tune_res <- tune_grid(
  tune_wf,
  resamples = readmitted_folds,
  grid = 10
)
tune_res
```



```{r}
tune_res %>%
  collect_metrics() %>%
  filter(.metric == "roc_auc") %>%
  select(mean, min_n, mtry) %>%
  pivot_longer(min_n:mtry,
    values_to = "value",
    names_to = "parameter"
  ) %>%
  ggplot(aes(value, mean, color = parameter)) +
  geom_point(show.legend = FALSE) +
  facet_wrap(~parameter, scales = "free_x") +
  labs(x = NULL, y = "AUC")
```



```{r}
rf_grid <- grid_regular(
  mtry(range = c(0,25)),
  min_n(range = c(10, 35)),
  levels = 5)

set.seed(456)

regular_res <- tune_grid(
  tune_wf,
  resamples = readmitted_folds,
  grid = rf_grid
)
best_auc <- select_best(regular_res, "roc_auc")
final_rf <- finalize_model(
  tune_spec,
  best_auc
)

final_rf
```



```{r}
final_rf %>%
  set_engine("ranger", importance = "permutation") %>%
  fit(readmitted ~ .,
    data = juice(tree_prep) 
  ) %>%
  vip(geom = "point")+
  labs(title = 'Importance Variables per Re-admition pacients')
```

Some Learning :

* Status change in the conditions not is determinant for Hospitalary - recidivism;
* Number inpatient has to do with the causes of new hospitalizations.
* Number of medications has a direct and important relationship for re-hospitalizations.

```{r}
final_wf <- workflow() %>%
  add_recipe(readmitted_rec) %>%
  add_model(final_rf)
final_res <- final_wf %>%
  last_fit(readmitted_split)

final_res %>%
  collect_metrics()
```


### Clusters

```{r}
database_pca<-data_select%>%
  filter(diabetesMed=='Yes')%>%
  select(race:medical_specialty,readmitted,num_lab_procedures:number_diagnoses)

database_pca
  
```


```{r}
pca_rec <- recipe(~., data = database_pca) %>%
  update_role(race, gender,age,weight,medical_specialty,readmitted,readmitted, new_role = "id") %>%
  step_normalize(all_predictors()) %>%
  step_pca(all_predictors())

pca_prep <- prep(pca_rec)

pca_prep
```


```{r}
tidied_pca <- tidy(pca_prep, 2)
tidied_pca %>%
  filter(component %in% paste0("PC", 1:5)) %>%
  mutate(component = fct_inorder(component)) %>%
  ggplot(aes(value, terms, fill = terms)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~component, nrow = 1) +
  labs(y = NULL)
```


```{r}
tidied_pca %>%
  filter(component %in% paste0("PC", 1:4)) %>%
  group_by(component) %>%
  top_n(8, abs(value)) %>%
  ungroup() %>%
  mutate(terms = reorder_within(terms, abs(value), component)) %>%
  ggplot(aes(abs(value), terms, fill = value > 0)) +
  geom_col() +
  facet_wrap(~component, scales = "free_y") +
  scale_y_reordered() +
  labs(
    x = "Absolute value of contribution",
    y = NULL, fill = "Readmitted?"
  )
```




```{r}
juice(pca_prep) %>%
  ggplot(aes(PC1, PC2, label = readmitted)) +
  geom_point(aes(color = race), alpha = 0.7, size = 1) +
  geom_text(check_overlap = TRUE, hjust = "inward",size=1) +
  labs(color = NULL)+
  labs(title = 'Cluster By Pca')+
  facet_wrap(~medical_specialty, scales = 'free')
```



```{r}
juice(pca_prep) %>%
  ggplot(aes(PC1, PC2, label = readmitted)) +
  geom_point(aes(color = gender), alpha = 0.7, size = 1) +
  geom_text(check_overlap = TRUE, hjust = "inward",size=2) +
  labs(color = NULL)+
  labs(title = 'Cluster By Pca')+
  facet_wrap(~medical_specialty, scales = 'free')
```

Final Comments:

* There are four cluster with PCA's;
* With  this informatio, the most important relevance are: Gender and medical_specialty.


